---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
<!-- use devtools::build_readme() -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fish4myeloma

<!-- badges: start -->
<!-- badges: end -->

**Early development 2024, breaking changes likely**
**Preliminary abnormality detection not yet finalised** 

**fish4myeloma** extracts Myeloma abnormalities from cytogenetic [FISH](https://en.wikipedia.org/wiki/Fluorescence_in_situ_hybridization) (Fluorescence in situ hybridization) data represented in strings according to the [ISCN](https://en.wikipedia.org/wiki/International_System_for_Human_Cytogenomic_Nomenclature) standardised nomenclature.


## Installation

You can install the development version of fish4myeloma from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("andysouth/fish4myeloma")
```

## Example

```{r example}
library(fish4myeloma)

## make some simple test data
fish_raw <- dplyr::tibble(test_id <- c(1:5),
                          fishstring=c("17p13(TP53x3) CKS1Bx3",
                                       "17p13(TP53x2) CKS1Bx2",
                                       "17p13(TP53x1) CKS1Bx1 FGFR3 con IGH",
                                       "IGH con MAF",
                                       "CCND1 con IGH"
                          ))

fish_processed <- fish_raw |>
   fish4del17p("fishstring") |>
   fish4cks1b("fishstring") |>
   fish4ighfgfr3("fishstring") |>
   fish4ighmaf("fishstring") |>
   fish4ighccnd1("fishstring")

knitr::kable(fish_processed)

```


